Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2020-03-26 paper/paper.tex
20200326 13:51
Signed-off-by: wangshiphys <wangshiphys@gmail.com>

The main effect of $\Gamma$ term on the Stripe-A and Stripe-D phase is tilting the moment orientation away from the cubic axes directions, yielding the Stripe-B and Stripe-C phase. Fig.~\ref{fig:Proabilities}(e) is a representative probability map for the Stripe-B phase. The probability takes maximum value at the direction determined by Eq.~\eqref{eq:S1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$. On the other hand, the case of the Stripe-C phase is rather different. The probability is clearly peaked at the direction given by Eq.~\eqref{eq:S0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig.~\ref{fig:Proabilities}(d)). Apart from the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the cluster GS, quantum flucations may take responsibilities for the reduced probability.

\section{\label{sec:SectionVI}Summary}
\textcolor{red}{Summary of our work. To be accomplished $\cdots \cdots$}

>>>>

The main effect of $\Gamma$ term on the Stripe-A and Stripe-D phase is tilting the moment orientation away from the cubic axes directions, yielding the Stripe-B and Stripe-C phase. Fig.~\ref{fig:Proabilities}(e) is a representative probability map for the Stripe-B phase. The probability takes maximum value at the direction determined by Eq.~\eqref{eq:v1}, which means that the moment direction changes with the model parameters $K$ and $\Gamma$. On the other hand, the case of the Stripe-C phase is rather different. The probability is clearly peaked at the direction given by Eq.~\eqref{eq:v0} with the maximum value $P_{max}$ considerably less than $\frac{1}{6}$ (see Fig.~\ref{fig:Proabilities}(d)). Apart from the overall reduction factor of $\frac{1}{6}$ due to the six possible stripe states being superposed in the cluster GS, quantum flucations may take responsibilities for the reduced probability.

\section{\label{sec:SectionVI}Summary}
In summary, by using classical Monte Carlo simulation and exact diagnoalization we map out the global phase diagram of both the classical and quantum $J-K-\Gamma$ model. The global phase diagram of the quantum model is analogus to its classical counterpart except a small area of QSL near the antiferromagetic $\Gamma$ point. We propose the QSL to be gapped based on the spin excitation spectrum. Apart from this QSL phase, we also provide detailed description of the distinctions between those collinear phases. Especially, we propose the GS of the antiferromagetic Kitaev model to be a stripe ordered state and the ordered moment along the $x, y, z$-axis direction.
